Verifying Hierarchical Cache Coherence Protocols: a theorem-prover based modular, reusable proof

### 2014-02-03 paper/Intuition.tex
stuff

\begin{inv}
\textit{inTransitChange}:
\begin{enumerate}
\item When a response is sent from a child $c$ at time $t$ for an address $a$,
and has not been received by the parent $p$ before time $t'$, $\forall t_i, t <
t_i \le t' @-> c.\state[a]$ at $t_i \le c.\state[a]$ at $t+1$ and $\forall t_i,
t \le t_i \le t' @->$ $p.\dstate[c][a]$ at $t_i \ge c.\state[a]$ at $t$.
\item When a response is sent from parent $p$ at time $t$ for an address $a$,
and has not been received by its child $c$ before time $t'$, $\forall t_i, t <
t_i \le t' @-> p.\dstate[c][a]$ at $t_i \ge p.\dstate[c][a]$ at $t+1$ and
$\forall t_i, t \le t_i \le t' @->$ $c.\state[a]$ at $t_i \le p.\dstate[c][a]$ at
$t$.
\end{enumerate}
\label{inTransitChange}
\end{inv}

@@

Using Invariants \ref{stateChange} to \ref{noTransit}, it is easy to prove
Invariant \ref{conservative}. If no response is in flight for an address, then
the parent's directory state of the cache for the address matches that of the
cache's state for that address. If there is a response from parent to child in
flight, then the corresponding directory at the parent will be no less than the
directory immediately after the response was sent and the state of the child
will be no greater than the directory immediately before the response was sent
(by Invariant \textit{inTransitChange}). By Invariant \textit{stateChange}, the
parent upgrades the directory when sending the response, thus conforming to
Invariant \textit{conservative}. Similarly, it can be shown that if there is a
response from child to parent, Invariant \textit{coservative} will hold.

>>>>

\begin{inv}
\textit{inTransitCondition}:
\begin{enumerate}
\item When a response is sent from a child $c$ at time $t$ for an address $a$,
and has not been received by the parent $p$ before time $t'$, $\forall t_i, t <
t_i \le t' @-> c.\state[a]$ at $t_i \le c.\state[a]$ at $t+1$ and $\forall t_i,
t \le t_i \le t' @->$ $p.\dstate[c][a]$ at $t_i \ge c.\state[a]$ at $t$.
\item When a response is sent from parent $p$ at time $t$ for an address $a$,
and has not been received by its child $c$ before time $t'$, $\forall t_i, t <
t_i \le t' @-> p.\dstate[c][a]$ at $t_i \ge p.\dstate[c][a]$ at $t+1$ and
$\forall t_i, t \le t_i \le t' @->$ $c.\state[a]$ at $t_i \le p.\dstate[c][a]$ at
$t$.
\end{enumerate}
\label{inTransitCondition}
\end{inv}

@@

Using Invariants \ref{stateChange} to \ref{noTransitEqual}, it is easy to prove
Invariant \textit{conservative}. If no response is in flight for an address, then
the parent's directory state of the cache for the address matches that of the
cache's state for that address. If there is a response from parent to child in
flight, then the corresponding directory at the parent will be no less than the
directory immediately after the response was sent and the state of the child
will be no greater than the directory immediately before the response was sent
(by Invariant \textit{inTransitCondition}). By Invariant \textit{stateChange}, the
parent upgrades the directory when sending the response, thus conforming to
Invariant \textit{conservative}. Similarly, it can be shown that if there is a
response from child to parent, Invariant \textit{conservative} will hold.

Proving Invariants \textit{inTransitCondition} and \textit{noTransitEqual},
needs two further invariants, along with Invariant \textit{stateChange}.

\begin{inv}
\textit{respFIFO}: Responses are received in the order in which they are sent,
for a source-destination pair.
\label{respFIFO}
\end{inv}

\begin{inv}
\textit{noCross}: A response from a cache to its child for an address can not
be in transit while another response from the same child to the parent for the
same address is in transit.
\label{noCross}
\end{inv}

Invariant \textit{inTransitCondition} can be proved as follows. Whenever a
response from a child to the parent is in transit, the parent can not send any
response to the child, or it will violate Invariant \textit{noCross}. Using the fact that
